High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2020-11-16 paper/main.tex
working on final pass through main text [WIP]

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/higher_order_sims}
  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    correlation matrix and the simulated correlation matrix at each
    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  All results in this figure used a Laplace kernel
    (width~$=20$).  \textbf{a. Constant correlations.}
    These first and second order dynamic correlation were
    simulated from datasets have a stable (unchanging) underlying correlation
    matrix.  \textbf{b. Random correlations.}  These first and second order dynamic correlation were
    simulated from datasets are
    generated using a new independently drawn correlation matrix at
    each new timepoint.  \textbf{c. Ramping correlations.}  These first and second order dynamic correlation were
    simulated from
    datasets are generated by smoothly varying the underlying
    correlations between the randomly drawn correlation matrices at
    the first and last timepoints and displays the
    correlations between the recovered dynamic correlations and the
  simulated correlation first and second order correlation matrices.   \textbf{d. Event-based correlations.}  These first and second order dynamic correlation were
    simulated from datasets are
    each generated using five randomly drawn correlation matrices that
    each remain stable for a fifth of the total timecourse.  The
    vertical lines denote event boundaries.}
  \label{fig:higher_order_sims}
\end{figure}

@@

Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields an
$\mathbf{X}$ whose columns reflect weighted combinations (or nonlinear
transformations) of the original columns of $\mathbf{Y}$.  This has
two main consequences.  First, with each repeated dimensionality
reduction, the resulting $\mathbf{X}_n$ has lower and lower fidelity
(with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
like without using dimensionality reduction to maintain tractability).
In other words, computing $\mathbf{X}_n$ is a lossy operation.
Second, whereas each column of $\mathbf{Y}_n$ may be mapped
directly onto specific pairs of columns of $\mathbf{X}_{n-1}$, the
columns of $\mathbf{X}_n$ reflect weighted combinations and/or
nonlinear transformations of the columns of $\mathbf{Y}_n$.  Many
dimensionality reduction algorithms are invertible (or approximately
invertible).  However, attempting to map a given $\mathbf{X}_n$ back
onto the original feature space of $\mathbf{X}_0$ will usually require
$\mathcal{O}(TK^{2n})$ space and therefore becomes intractable
as $n$ or $K$ grow large.

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figs/higher_order_sims}
  \caption{\textbf{Recovery of simulated first-order and second-order dynamic correlations.}  Each panel displays the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices at each
    timepoint and for each synthetic dataset.  (The averages are taken across 10 different
    randomly generated synthetic datasets of the given category.)
    Error ribbons denote 95\% confidence intervals (taken across
    datasets).  For a complete description of each synthetic dataset,
    see \textit{Synthetic data: simulating dynamic higher-order
      correlations}.  All estimates represented in this figure were
    computed using a Laplace kernel
    (width~$=20$).  \textbf{a. Constant correlations.}  These datasets
    have stable (unchanging) underlying second-order correlation
    matrices.  \textbf{b. Random correlations.} These datasets are
    generated using a new independently drawn second-order correlation
    matrix at each timepoint.  \textbf{c. Ramping correlations.}
    These datasets are generated by smoothly varying the underlying
    second-order correlations between the randomly drawn correlation
    matrices at the first and last timepoints.  \textbf{d. Event-based
      correlations.}  These datasets are each generated using five
    randomly drawn second-order correlation matrices that each remain
    stable for a fifth of the total timecourse.  The
    vertical lines denote event boundaries.}
  \label{fig:higher_order_sims}
\end{figure}

@@

Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields an
$\mathbf{X}$ whose columns reflect weighted combinations (or nonlinear
transformations) of the original columns of $\mathbf{Y}$.  This has
two main consequences.  First, with each repeated dimensionality
reduction, the resulting $\mathbf{X}_n$ has lower and lower fidelity
(with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
like without using dimensionality reduction to maintain tractability).
In other words, computing $\mathbf{X}_n$ is a lossy operation.
Second, whereas each column of $\mathbf{Y}_n$ may be mapped
directly onto specific pairs of columns of $\mathbf{X}_{n-1}$, the
columns of $\mathbf{X}_n$ reflect weighted combinations and/or
nonlinear transformations of the columns of $\mathbf{Y}_n$.  Many
dimensionality reduction algorithms are invertible (or approximately
invertible).  However, attempting to map a given $\mathbf{X}_n$ back
onto the original feature space of $\mathbf{X}_0$ will usually require
$\mathcal{O}(TK^{2^n})$ space and therefore becomes intractable
as $n$ or $K$ grow large.
